---
title: "stance_detection_viz"
author: "Laura Sørine Voldgaard"
date: "2024-11-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# libraries
pacman::p_load(tidyverse, extrafont, cowplot, stringr)

getwd()
```

```{r}
# load data
sd <- read.csv("stance_detection_result.csv")
```

```{r}
# cleaning
sd <- sd %>% 
  rename('for' = 'for.') # removing the dot in for.
```


*Plots*

Number of articles per stance
```{r}
# bar plot to count articles for each stance
stance_total <- ggplot(sd, aes(x = stance, fill = stance)) +
  geom_bar() +
  labs(title = "Number of Articles by Stance", x = "Stance", y = "Number of Articles") +
  theme_minimal()
stance_total

```

```{r}
# save plot
ggsave("stance_total.png", plot = stance_total, width = 8, height = 6, dpi = 300)  # Save as PNG
```





Number of articles per stance over time
```{r}
# Convert `date` to Date format and extract the year
sd <- sd %>%
  mutate(year = as.numeric(format(as.Date(date), "%Y")))

# Group by year and stance, then count the number of articles
sd_grouped <- sd %>%
  group_by(year, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Plot the development over years
ggplot(sd_grouped, aes(x = year, y = article_count, color = stance, group = stance)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  labs(title = "Development of Articles by Stance Over Time",
       x = "Year",
       y = "Number of Articles",
       color = "Stance") +
  theme_cowplot()

```

Number of articles per stance over time - proportional normalization
```{r}
# Convert `date` to Date format and extract the year
sd <- sd %>%
  mutate(year = as.numeric(format(as.Date(date), "%Y")))

# Group by year and stance, then count the number of articles
sd_grouped <- sd %>%
  group_by(year, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Compute the total number of articles per year
year_totals <- sd_grouped %>%
  group_by(year) %>%
  summarise(total_articles = sum(article_count))

# Merge the totals back into the grouped data
sd_normalized <- sd_grouped %>%
  left_join(year_totals, by = "year") %>%
  mutate(proportion = article_count / total_articles)

# Plot the proportion of stances over time
ggplot(sd_normalized, aes(x = year, y = proportion, color = stance, group = stance)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  labs(title = "Development of Stances Over Time (Normalized)",
       x = "Year",
       y = "Proportion of Articles",
       color = "Stance") +
  theme_cowplot()

```









Number of articles per stance, CNN and Fox News
```{r}
# Group by source and stance, then count the number of articles
sd_static <- sd %>%
  group_by(leaning, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Create a custom color palette
custom_colors <- c("Left" = "blue", "Right" = "red")


# Create a grouped bar plot
ggplot(sd_static, aes(x = stance, y = article_count, fill = leaning)) +
  geom_bar(stat = "identity", position = "dodge") +
    scale_fill_manual(values = custom_colors) +  # Apply custom colors
  labs(title = "Number of Articles by Stance and Leaning",
       x = "Stance",
       y = "Number of Articles",
       fill = "Leaning") +
  theme_minimal()

```


Number of articles per stance, CNN and Fox News - proportional normalization
```{r}
# Group by source and stance, then count the number of articles
sd_static <- sd %>%
  group_by(leaning, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Compute the total number of articles per source
leaning_totals <- sd_static %>%
  group_by(leaning) %>%
  summarise(total_articles = sum(article_count))

# Merge the totals back into the grouped data
sd_normalized <- sd_static %>%
  left_join(leaning_totals, by = "leaning") %>%
  mutate(proportion = article_count / total_articles)

# Create a custom color palette
custom_colors <- c("Left" = "blue", "Right" = "red")


# Create a grouped bar plot with custom colors
stance_static_leaning <- ggplot(sd_normalized, aes(x = stance, y = proportion, fill = leaning)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = custom_colors) +  # Apply custom colors
  labs(title = "Proportion of Articles by Stance and Source (normalized)",
       x = "Stance",
       y = "Proportion of Articles",
       fill = "Leaning") +
  theme_minimal()

stance_static_leaning

```

```{r}
# save plot
ggsave("stance_static_leaning.png", plot = stance_static_leaning, width = 8, height = 6, dpi = 300)  # Save as PNG
```



Number of articles per stance over time (year) CNN and Fox News (proportional normalization)
```{r}
# Convert `date` to Date format and extract the year
sd <- sd %>%
  mutate(year = as.numeric(format(as.Date(date), "%Y")))

# Group by year, leaning, and stance, then count the number of articles
sd_grouped <- sd %>%
  group_by(year, leaning, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Compute the total number of articles per source and year
leaning_year_totals <- sd_grouped %>%
  group_by(year, leaning) %>%
  summarise(total_articles = sum(article_count), .groups = "drop")

# Merge the totals back into the grouped data
sd_normalized <- sd_grouped %>%
  left_join(leaning_year_totals, by = c("year", "leaning")) %>%
  mutate(proportion = article_count / total_articles)

# Filter for CNN and Fox News only
sd_filtered <- sd_normalized %>%
  filter(leaning %in% c("Left", "Right"))

# Create a line plot showing proportions over time
ggplot(sd_filtered, aes(x = year, y = proportion, color = stance, group = stance)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  facet_wrap(~leaning, ncol = 1) +  # Separate plots for CNN and Fox News
  scale_color_manual(values = c("green", "orange", "darkcyan")) +  # Customize colors for stances
  labs(title = "Proportion of Stances Over Time by Leaning",
       x = "Year",
       y = "Proportion of Articles",
       color = "Leaning") +
  theme_minimal()

```



Number of articles per stance over time (month) CNN and Fox News (proportional normalization)
```{r}
# Convert `date` to Date format and extract the month-year
sd <- sd %>%
  mutate(month_year = format(as.Date(date), "%Y-%m"))  # Extract month-year in "YYYY-MM" format

# Group by month-year, source, and stance, then count the number of articles
sd_grouped <- sd %>%
  group_by(month_year, leaning, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Compute the total number of articles per source and month-year
leaning_month_totals <- sd_grouped %>%
  group_by(month_year, leaning) %>%
  summarise(total_articles = sum(article_count), .groups = "drop")

# Merge the totals back into the grouped data
sd_normalized <- sd_grouped %>%
  left_join(leaning_month_totals, by = c("month_year", "leaning")) %>%
  mutate(proportion = article_count / total_articles)

# Filter for CNN and Fox News only
sd_filtered <- sd_normalized %>%
  filter(leaning %in% c("Left", "Right"))

# Convert month_year to a date format for proper x-axis ordering
sd_filtered <- sd_filtered %>%
  mutate(month_year = as.Date(paste0(month_year, "-01")))  # Convert to Date format

# Create a line plot showing proportions over time (month-year granularity)
ggplot(sd_filtered, aes(x = month_year, y = proportion, color = stance, group = stance)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  facet_wrap(~leaning, ncol = 1) +  # Separate plots for CNN and Fox News
  scale_color_manual(values = c("green", "orange", "darkcyan")) +  # Customize colors for stances
  labs(title = "Proportion of Stances Over Time by Leaning (normalized)",
       x = "Month-Year",
       y = "Proportion of Articles",
       color = "Leaning") +
  theme_minimal() +
  scale_x_date(date_labels = "%b %y", date_breaks = "5 months")  # Format x-axis labels

```


73 day interval instead of each month
```{r}
# Convert `date` to Date format and compute 73-day intervals
sd <- sd %>%
  mutate(
    date = as.Date(date),  # Ensure `date` is in Date format
    interval_start = as.Date("1970-01-01") + ((as.numeric(date - as.Date("1970-01-01")) %/% 73) * 73)  # Compute interval start
  )

# Group by 73-day intervals, source, and stance, then count the number of articles
sd_grouped <- sd %>%
  group_by(interval_start, leaning, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Compute the total number of articles per source and interval
leaning_interval_totals <- sd_grouped %>%
  group_by(interval_start, leaning) %>%
  summarise(total_articles = sum(article_count), .groups = "drop")

# Merge the totals back into the grouped data
sd_normalized <- sd_grouped %>%
  left_join(leaning_interval_totals, by = c("interval_start", "leaning")) %>%
  mutate(proportion = article_count / total_articles)

# Filter for Left and Right only
sd_filtered <- sd_normalized %>%
  filter(leaning %in% c("Left", "Right"))

# Create a line plot showing proportions over time (73-day intervals)
stance_dynamic_leaning <- ggplot(sd_filtered, aes(x = interval_start, y = proportion, color = stance, group = stance)) +
  geom_line(size = 1.2) +
  geom_point(size = 2) +
  facet_wrap(~leaning, ncol = 1) +  # Separate plots for Left and Right
  scale_color_manual(values = c("green", "orange", "darkcyan")) +  # Customize colors for stances
  labs(
    title = "Proportion of Stances Over Time by Leaning (normalized)",
    x = "Time Interval (73 Days)",
    y = "Proportion of Articles",
    color = "Stance"
  ) +
  theme_minimal() +
  scale_x_date(date_labels = "%b %y", date_breaks = "5 months")  # Format x-axis labels

stance_dynamic_leaning
```

```{r}
# save plot
ggsave("stance_dynamic_leaning.png", plot = stance_dynamic_leaning, width = 8, height = 6, dpi = 300)  # Save as PNG
```









*Working with uncertainty*

Ternary plot of article stance probabilities - together
```{r}
# Install the 'ggtern' package if not already installed
install.packages("ggtern")

library(ggtern)

# Create a custom color palette
custom_colors <- c("Left" = "blue", "Right" = "red")

# Ternary plot
ggtern(data = sd, aes(x = `for`, y = `neutral.toward`, z = against)) +
  geom_point(aes(color = leaning), size = 2, alpha = 0.7) +
  scale_color_manual(values = custom_colors) +  # Apply custom colors
  labs(title = "Ternary Plot of Article Stance Probabilities",
       x = "For",
       y = "Neutral",
       z = "Against") +
  theme_minimal()

```


Ternary plot of article stance probabilities - for Left nad Right separately - no line
```{r}
# Install the 'ggtern' package if not already installed
install.packages("ggtern")

library(ggtern)
library(dplyr)  # For data manipulation

# Create a custom color palette
custom_colors <- c("Left" = "blue", "Right" = "red")

# Filter data for Left-leaning articles and plot
left_plot <- ggtern(
  data = filter(sd, leaning == "Left"),  # Filter for Left-leaning
  aes(x = `for`, y = `neutral.toward`, z = against)
) +
  geom_point(color = custom_colors["Left"], size = 2, alpha = 0.7) +
  labs(
    title = "Ternary Plot of Article Stance Probabilities (Left-Leaning)",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

# Filter data for Right-leaning articles and plot
right_plot <- ggtern(
  data = filter(sd, leaning == "Right"),  # Filter for Right-leaning
  aes(x = `for`, y = `neutral.toward`, z = against)
) +
  geom_point(color = custom_colors["Right"], size = 2, alpha = 0.7) +
  labs(
    title = "Ternary Plot of Article Stance Probabilities (Right-Leaning)",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

# Print the plots
print(left_plot)
print(right_plot)

```



















Ternary Plot of Article Stance Probabilities - with line
```{r}
# Install and load the required ggtern package
# install.packages("ggtern")
#library(ggtern)
#library(dplyr)

# Create a custom color palette
custom_colors <- c("Left" = "blue", "Right" = "red")

# Define coordinates for the lines that split the triangle into 3 equal regions
split_lines <- data.frame(
  x_start = c(0.5, 0, 0.5),   # Midpoints of triangle edges
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),  # Center point
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Filter data for Left-leaning articles and create the plot
left_plot <- ggtern(
  data = filter(sd, leaning == "Left"),  # Filter for Left-leaning
  aes(x = `for`, y = `neutral.toward`, z = against)
) +
  geom_point(color = custom_colors["Left"], size = 1.6, alpha = 0.7) +  # Points
  geom_segment(data = split_lines, inherit.aes = FALSE,  # Add dividing lines
               aes(x = x_start, y = y_start, z = z_start, 
                   xend = x_end, yend = y_end, zend = z_end), 
               color = "black", size = 0.7) +  # Thin lines
  labs(
    title = "Left-Leaning",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

# Filter data for Right-leaning articles and create the plot
right_plot <- ggtern(
  data = filter(sd, leaning == "Right"),  # Filter for Right-leaning
  aes(x = `for`, y = `neutral.toward`, z = against)
) +
  geom_point(color = custom_colors["Right"], size = 1.6, alpha = 0.7) +  # Points
  geom_segment(data = split_lines, inherit.aes = FALSE,  # Add dividing lines
               aes(x = x_start, y = y_start, z = z_start, 
                   xend = x_end, yend = y_end, zend = z_end), 
               color = "black", size = 0.7) +  # Thin lines
  labs(
    title = "Right-Leaning",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

# Print the plots
print(left_plot)
print(right_plot)

```

```{r}
# save plot
ggsave("right_plot.png", plot = right_plot, width = 8, height = 6, dpi = 300)  # Save as PNG
ggsave("left_plot.png", plot = left_plot, width = 8, height = 6, dpi = 300)  # Save as PNG

```



Ternary Plot of Article Stance Probabilities - Grid
```{r}
# Install and load required packages
# install.packages("ggtern")
# install.packages("gridExtra")
library(ggtern)
library(dplyr)
library(gridExtra)

# Create a custom color palette
custom_colors <- c("Left" = "blue", "Right" = "red")

# Define coordinates for the lines that split the triangle into 3 equal regions
split_lines <- data.frame(
  x_start = c(0.5, 0, 0.5),   # Midpoints of triangle edges
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),  # Center point
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Filter data for Left-leaning articles and create the plot
left_plot <- ggtern(
  data = filter(sd, leaning == "Left"),  # Filter for Left-leaning
  aes(x = `for`, y = `neutral.toward`, z = against)
) +
  geom_point(color = custom_colors["Left"], size = 1.5, alpha = 0.7) +  # Points
  geom_segment(data = split_lines, inherit.aes = FALSE,  # Add dividing lines
               aes(x = x_start, y = y_start, z = z_start, 
                   xend = x_end, yend = y_end, zend = z_end), 
               color = "black", size = 0.7) +  # Thin lines
  labs(
    title = "Left-Leaning",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

# Filter data for Right-leaning articles and create the plot
right_plot <- ggtern(
  data = filter(sd, leaning == "Right"),  # Filter for Right-leaning
  aes(x = `for`, y = `neutral.toward`, z = against)
) +
  geom_point(color = custom_colors["Right"], size = 1.5, alpha = 0.7) +  # Points
  geom_segment(data = split_lines, inherit.aes = FALSE,  # Add dividing lines
               aes(x = x_start, y = y_start, z = z_start, 
                   xend = x_end, yend = y_end, zend = z_end), 
               color = "black", size = 0.7) +  # Thin lines
  labs(
    title = "Right-Leaning",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

# Combine the plots into a grid
grid.arrange(left_plot, right_plot, ncol = 2)

```




HEATMAP
```{r}
# Install and load required libraries
# install.packages("ggtern")
# install.packages("dplyr")
# install.packages("hexbin")
#library(ggtern)
#library(dplyr)
#library(ggplot2)

# Define coordinates for the dividing lines
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to bin data into heatmap tiles
create_heatmap_manual <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  # Manually bin the data into small triangles
  binned_data <- filtered_data %>%
    mutate(
      x_bin = cut(`for`, breaks = seq(0, 1, by = 0.05)),   # Bin the "For" axis
      y_bin = cut(`neutral.toward`, breaks = seq(0, 1, by = 0.05))  # Bin the "Neutral" axis
    ) %>%
    group_by(x_bin, y_bin) %>%
    summarize(count = n(), .groups = "drop") %>%
    mutate(density = count / sum(count))  # Normalize density

  # Convert bin labels to numeric for plotting
  binned_data <- binned_data %>%
    mutate(
      x = as.numeric(sub("\\((.+),.*", "\\1", x_bin)) + 0.025,
      y = as.numeric(sub("\\((.+),.*", "\\1", y_bin)) + 0.025
    )
  
  # Plot the heatmap using geom_tile
  ggtern() +
    geom_tile(data = binned_data, aes(x = x, y = y, z = 1 - x - y, fill = density)) +
    scale_fill_gradient(low = "white", high = color, name = "Density") +
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start,
                     xend = x_end, yend = y_end, zend = z_end),
                 color = "black", size = 0.7) +
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal()
}

# Plot for Left-Leaning articles
left_heatmap <- create_heatmap_manual(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Plot for Right-Leaning articles
right_heatmap <- create_heatmap_manual(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print the plots
print(left_heatmap)
print(right_heatmap)

```




```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Define coordinates for the dividing lines
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to create a heatmap-based ternary plot with normalized bins
create_heatmap_ternary <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  ggtern(data = filtered_data, 
         aes(x = `for`, y = `neutral.toward`, z = against)) +
    stat_bin_tern(geom = "polygon", 
                  aes(fill = ..count..), bins = 20) +  # Bin the data and compute counts
    scale_fill_gradient(low = "white", high = color, name = "Count") +  # Color scale
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start,
                     xend = x_end, yend = y_end, zend = z_end),
                 color = "black", size = 0.7) +  # Add dividing lines
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal() +
    theme(legend.position = "right")  # Place legend on the right
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print the plots
print(left_heatmap)
print(right_heatmap)

```





```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Define coordinates for dividing lines
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to create a heatmap-based ternary plot
create_heatmap_ternary <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  ggtern(data = filtered_data, 
         aes(x = `for`, y = `neutral.toward`, z = against)) +
    stat_summary_tern(geom = "polygon", 
                      fun = function(x, y, z, w = NULL) { length(x) },  # Count points
                      aes(fill = ..value..), bins = 20) +  # Heatmap bins
    scale_fill_gradient(low = "white", high = color, name = "Count") +  # Color scale
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start,
                     xend = x_end, yend = y_end, zend = z_end),
                 color = "black", size = 0.7) +  # Add dividing lines
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal() +
    theme(legend.position = "right")  # Place legend on the right
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print individual heatmaps
print(left_heatmap)
print(right_heatmap)

```

```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Define coordinates for the dividing lines
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to create a heatmap-based ternary plot
create_hexbin_heatmap <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  ggtern(data = filtered_data, 
         aes(x = `for`, y = `neutral.toward`, z = against)) +
    stat_bin_hex(bins = 20, aes(fill = ..count..)) +  # Use hexagonal bins for counts
    scale_fill_gradient(low = "white", high = color, name = "Count") +  # Heatmap color
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start,
                     xend = x_end, yend = y_end, zend = z_end),
                 color = "black", size = 0.7) +  # Add dividing lines
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal() +
    theme(legend.position = "right")  # Place legend on the right
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_hexbin_heatmap(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_hexbin_heatmap(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print individual heatmaps
print(left_heatmap)
print(right_heatmap)

```



Closest so far:
```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Define coordinates for the lines that split the triangle into 3 equal regions
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to create individual heatmap-based ternary plot
create_heatmap_ternary <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  ggtern(data = filtered_data, 
         aes(x = `for`, y = `neutral.toward`, z = against)) +
    stat_density_tern(geom = "polygon", 
                      aes(fill = ..level..),  # Use ..level.. for density mapping
                      bins = 20) +            # Number of bins for granularity
    scale_fill_gradient(low = "white", high = color) +  # Heatmap color gradient
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start, 
                     xend = x_end, yend = y_end, zend = z_end), 
                 color = "black", size = 0.7) +  # Add dividing lines
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against",
      fill = "Density"
    ) +
    theme_minimal()
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Left", color = "blue", 
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Right", color = "red", 
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print individual heatmaps
print(left_heatmap)
print(right_heatmap)

```





```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Define coordinates for the lines that split the triangle into 3 equal regions
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to create individual heatmap-based ternary plot
create_heatmap_ternary <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  ggtern(data = filtered_data, 
         aes(x = `for`, y = `neutral.toward`, z = against)) +
    stat_density_tern(geom = "polygon", 
                      aes(fill = ..level..),  # Map density levels to fill
                      bins = 20,             # Number of bins for granularity
                      bdl = 0.01) +          # Set below-detection-limit (handles fringes)
    scale_fill_gradient(low = "white", high = color, name = "Density", 
                        breaks = seq(0, max(filtered_data$`for`), length.out = 5)) + 
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start, 
                     xend = x_end, yend = y_end, zend = z_end),
                 color = "black", size = 0.7) +  # Add dividing lines
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against",
      fill = "Density"
    ) +
    theme_minimal()
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Left", color = "blue", 
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Right", color = "red", 
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print individual heatmaps
print(left_heatmap)
print(right_heatmap)

```




```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Define coordinates for the lines that split the triangle into 3 equal regions
split_lines <- data.frame(
  x_start = c(0.5, 0, 1),
  y_start = c(0, 0.5, 0.5),
  z_start = c(0.5, 0.5, 0),
  x_end = c(0.5, 0.5, 0.5),
  y_end = c(0.5, 0.5, 0.5),
  z_end = c(0.5, 0.5, 0.5)
)

# Function to create a normalized heatmap for ternary plot
create_normalized_heatmap <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  total_points <- nrow(filtered_data)  # Total number of points for normalization
  
  ggtern(data = filtered_data, 
         aes(x = `for`, y = `neutral.toward`, z = against)) +
    stat_bin_hex(
      bins = 20,  # Number of bins for granularity
      aes(fill = ..count.. / total_points)  # Normalize bin count by total points
    ) +
    scale_fill_gradient(low = "white", high = color, name = "Proportion") +  # Gradient fill
    geom_segment(data = split_lines, inherit.aes = FALSE,
                 aes(x = x_start, y = y_start, z = z_start, 
                     xend = x_end, yend = y_end, zend = z_end),
                 color = "black", size = 0.7) +  # Add dividing lines
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal()
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_normalized_heatmap(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_normalized_heatmap(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print the heatmaps
print(left_heatmap)
print(right_heatmap)

```




```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Function to manually bin the data into grid cells and plot the heatmap
create_heatmap_ternary <- function(data, leaning, color, title) {
  # Filter data for the selected leaning
  filtered_data <- data %>% filter(leaning == leaning)
  
  # Define the grid resolution
  grid_res <- 20  # Number of bins along each axis
  
  # Create grid coordinates
  grid <- expand.grid(
    x = seq(0, 1, length.out = grid_res),
    y = seq(0, 1, length.out = grid_res)
  ) %>%
    filter(x + y <= 1) %>%  # Ensure points are within the ternary space
    mutate(z = 1 - x - y)   # Compute z-coordinate
  
  # Function to count points within each grid cell
  grid_counts <- grid %>%
    rowwise() %>%
    mutate(count = sum(
      abs(filtered_data$`for` - x) < 1 / grid_res &
      abs(filtered_data$`neutral.toward` - y) < 1 / grid_res &
      abs(filtered_data$against - z) < 1 / grid_res
    )) %>%
    ungroup() %>%
    mutate(proportion = count / nrow(filtered_data))  # Normalize to get proportions

  # Plot the heatmap
  ggtern(data = grid_counts, aes(x = x, y = y, z = z)) +
    geom_polygon(aes(group = interaction(x, y), fill = proportion)) +
    scale_fill_gradient(low = "white", high = color, name = "Proportion") +
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal()
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print the heatmaps
print(left_heatmap)
print(right_heatmap)

```



```{r}
# Install and load required libraries
library(ggtern)
library(dplyr)

# Function to normalize data and plot the heatmap
create_heatmap_ternary <- function(data, leaning, color, title) {
  # Filter and normalize data for the selected leaning
  filtered_data <- data %>%
    filter(leaning == leaning) %>%
    rowwise() %>%
    mutate(
      total = `for` + `neutral.toward` + against,
      `for` = `for` / total,
      `neutral.toward` = `neutral.toward` / total,
      against = against / total
    ) %>%
    ungroup()
  
  # Define the grid resolution
  grid_res <- 50  # Finer grid for better resolution
  
  # Create grid coordinates
  grid <- expand.grid(
    x = seq(0, 1, length.out = grid_res),
    y = seq(0, 1, length.out = grid_res)
  ) %>%
    filter(x + y <= 1) %>%  # Ensure points are within the ternary space
    mutate(z = 1 - x - y)   # Compute z-coordinate
  
  # Count points within each grid cell
  grid_counts <- grid %>%
    rowwise() %>%
    mutate(count = sum(
      abs(filtered_data$`for` - x) < 1 / grid_res &
      abs(filtered_data$`neutral.toward` - y) < 1 / grid_res &
      abs(filtered_data$against - z) < 1 / grid_res
    )) %>%
    ungroup() %>%
    mutate(proportion = count / nrow(filtered_data))  # Normalize to get proportions
  
  # Plot the heatmap
  ggtern(data = grid_counts, aes(x = x, y = y, z = z)) +
    geom_polygon(aes(group = interaction(x, y), fill = proportion)) +
    scale_fill_gradient(low = "white", high = color, name = "Proportion") +
    labs(
      title = title,
      x = "For",
      y = "Neutral",
      z = "Against"
    ) +
    theme_minimal()
}

# Heatmap for Left-Leaning articles
left_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Left", color = "blue",
  title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)"
)

# Heatmap for Right-Leaning articles
right_heatmap <- create_heatmap_ternary(
  data = sd, leaning = "Right", color = "red",
  title = "Ternary Heatmap of Article Stance Probabilities (Right-Leaning)"
)

# Print the heatmaps
print(left_heatmap)
print(right_heatmap)

```





```{r}
# Install and load required libraries
# install.packages("ggtern")
library(ggtern)
library(dplyr)

# Filter the Left-Leaning data
left_data <- sd %>%
  filter(leaning == "Left") %>%
  rowwise() %>%
  mutate(
    total = `for` + `neutral.toward` + against,
    `for` = `for` / total,
    `neutral.toward` = `neutral.toward` / total,
    against = against / total
  ) %>%
  ungroup()

# Define the grid resolution
grid_res <- 50  # Number of bins along each axis

# Create a grid of coordinates within the ternary space
grid <- expand.grid(
  x = seq(0, 1, length.out = grid_res),
  y = seq(0, 1, length.out = grid_res)
) %>%
  filter(x + y <= 1) %>%  # Ensure points are inside the ternary triangle
  mutate(z = 1 - x - y)   # Compute the z-coordinate

# Count the number of data points within each grid cell
grid_counts <- grid %>%
  rowwise() %>%
  mutate(count = sum(
    abs(left_data$`for` - x) < 1 / grid_res &
    abs(left_data$`neutral.toward` - y) < 1 / grid_res &
    abs(left_data$against - z) < 1 / grid_res
  )) %>%
  ungroup() %>%
  mutate(proportion = count / nrow(left_data))  # Normalize counts to get proportions

# Plot the heatmap
ggtern(data = grid_counts, aes(x = x, y = y, z = z)) +
  geom_polygon(aes(group = interaction(x, y), fill = proportion)) +
  scale_fill_gradient(low = "white", high = "blue", name = "Proportion") +
  labs(
    title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

```






```{r}
# Install and load required libraries
library(ggtern)
library(dplyr)

# Step 1: Filter and normalize the Left-Leaning data
left_data <- sd %>%
  filter(leaning == "Left") %>%
  rowwise() %>%
  mutate(
    total = `for` + `neutral.toward` + against,
    `for` = `for` / total,
    `neutral.toward` = `neutral.toward` / total,
    against = against / total
  ) %>%
  ungroup()

# Check that the data is normalized
print(head(left_data))

# Step 2: Define a coarser grid resolution
grid_res <- 10  # Coarser resolution for debugging

# Create grid of ternary coordinates
grid <- expand.grid(
  x = seq(0, 1, length.out = grid_res),
  y = seq(0, 1, length.out = grid_res)
) %>%
  filter(x + y <= 1) %>%
  mutate(z = 1 - x - y)

# Step 3: Count points within each grid cell
grid_counts <- grid %>%
  rowwise() %>%
  mutate(count = sum(
    abs(left_data$`for` - x) < 1 / grid_res &
    abs(left_data$`neutral.toward` - y) < 1 / grid_res &
    abs(left_data$against - z) < 1 / grid_res
  )) %>%
  ungroup() %>%
  mutate(proportion = count / nrow(left_data))  # Normalize counts

# Step 4: Check grid counts
print(head(grid_counts))

# Step 5: Plot the heatmap
ggtern(data = grid_counts, aes(x = x, y = y, z = z)) +
  geom_polygon(aes(group = interaction(x, y), fill = proportion), color = "grey80") +
  scale_fill_gradient(low = "white", high = "blue", name = "Proportion") +
  labs(
    title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

```








```{r}
# Install and load required libraries
library(ggtern)
library(dplyr)

# Step 1: Filter Left-Leaning data
left_data <- sd %>%
  filter(leaning == "Left")

# Step 2: Define grid resolution and round data to grid centers
grid_res <- 0.05  # Grid step size (coarser for better visualization)

# Round data to the nearest grid center
binned_data <- left_data %>%
  mutate(
    x = round(`for` / grid_res) * grid_res,
    y = round(`neutral.toward` / grid_res) * grid_res,
    z = round(against / grid_res) * grid_res
  ) %>%
  group_by(x, y, z) %>%
  summarize(count = n(), .groups = "drop") %>%
  mutate(proportion = count / sum(count))  # Normalize counts to proportions

# Step 3: Plot using geom_tile for heatmap
ggtern(data = binned_data, aes(x = x, y = y, z = z)) +
  geom_tile(aes(fill = proportion)) +
  scale_fill_gradient(low = "white", high = "blue", name = "Proportion") +
  labs(
    title = "Ternary Heatmap of Article Stance Probabilities (Left-Leaning)",
    x = "For",
    y = "Neutral",
    z = "Against"
  ) +
  theme_minimal()

```


























lol what is this
```{r}
library(GGally)

# Parallel coordinates plot
ggparcoord(data = sd, 
           columns = c(6, 7, 8), # Assuming these are 'for', 'neutral', and 'against'
           groupColumn = "leaning",
           scale = "globalminmax") +
  scale_color_manual(values = custom_colors) +
  labs(
    title = "Parallel Coordinate Plot of Stance Probabilities",
    x = "Stance",
    y = "Probability"
  ) +
  theme_minimal()

```



```{r}
install.packages("ggradar")
pacman::p_load(ggradar)

# Aggregate probabilities for Left and Right groups
agg_data <- sd %>%
  group_by(leaning) %>%
  summarise(
    `For` = mean(`for`),
    `Neutral` = mean(`neutral.toward`),
    `Against` = mean(against)
  )

# Convert to radar chart-friendly format
agg_data <- as.data.frame(agg_data)
agg_data <- agg_data %>%
  pivot_longer(-leaning, names_to = "stance", values_to = "value") %>%
  pivot_wider(names_from = stance, values_from = value)

# Radar chart
ggradar(agg_data, 
        group.colours = c("blue", "red")) +
  labs(
    title = "Radar Chart of Average Probabilities by Leaning"
  )

```





```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

# Aggregate the data for Left and Right groups
agg_data <- sd %>%
  group_by(leaning) %>%
  summarise(
    `For` = mean(`for`),
    `Neutral` = mean(`neutral.toward`),
    `Against` = mean(against)
  )

# Reshape the data for ggplot
radar_data <- agg_data %>%
  pivot_longer(-leaning, names_to = "stance", values_to = "value") %>%
  mutate(stance = factor(stance, levels = c("For", "Neutral", "Against")))  # Ensure proper order

# Add a row to "close" the polygons (for radar chart)
radar_data <- bind_rows(radar_data, radar_data %>% filter(stance == "For"))

# Radar plot with custom colors
ggplot(radar_data, aes(x = stance, y = value, group = leaning, color = leaning, fill = leaning)) +
  geom_polygon(alpha = 0.2, size = 1) +  # Fill and outline for polygons
  geom_line(size = 1) +
  geom_point(size = 3) +
  coord_polar() +
  scale_color_manual(values = c("Left" = "blue", "Right" = "red")) +  # Custom colors for lines
  scale_fill_manual(values = c("Left" = "blue", "Right" = "red")) +   # Custom colors for fill
  scale_y_continuous(limits = c(0, 1)) +  # Adjust scale if probabilities are between 0 and 1
  labs(
    title = "Radar Chart of Average Probabilities by Leaning",
    x = "",
    y = "Probability"
  ) +
  theme_minimal()

```


```{r}
# Calculate average probabilities
heatmap_data <- sd %>%
  group_by(leaning) %>%
  summarise(
    `For` = mean(`for`),
    `Neutral` = mean(`neutral.toward`),
    `Against` = mean(against)
  ) %>%
  pivot_longer(-leaning, names_to = "stance", values_to = "probability")

# Heatmap
ggplot(heatmap_data, aes(x = stance, y = leaning, fill = probability)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(
    title = "Heatmap of Stance Probabilities by Leaning",
    x = "Stance",
    y = "Leaning",
    fill = "Probability"
  ) +
  theme_minimal()

```



























```{r}
# Reshape the data to long format for visualization
sd_long <- sd %>%
  select(textID, source, `for`, neutral, against) %>%
  pivot_longer(cols = c("for", "neutral", "against"),
               names_to = "stance",
               values_to = "probability")

# Stacked bar plot
ggplot(sd_long, aes(x = textID, y = probability, fill = stance)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("blue", "gray", "red")) +  # Customize colors
  labs(title = "Uncertainty in Article Stances",
       x = "Article ID",
       y = "Probability",
       fill = "Stance") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),  # Hide x-axis labels for clarity
        axis.ticks.x = element_blank())

```







Found this code online:P
'''
require(ggplot2)
require(ggtern)
require(MASS) 
require(scales)
require(plyr)

palette <- c( "#FF9933", "#002C54", "#3375B2", "#CCDDEC", "#BFBFBF", "#000000")

# Example data
# sig <- matrix(c(3,0,0,2),2,2)
# data <- data.frame(mvrnorm(n=10000, rep(2, 2), sig))
# data$X1 <- data$X1/max(data$X1)
# data$X2 <- data$X2/max(data$X2)
# data$X1[which(data$X1<0)] <- runif(length(data$X1[which(data$X1<0)]))
# data$X2[which(data$X2<0)] <- runif(length(data$X2[which(data$X2<0)]))

# Print 2d heatmap
heatmap2d <- function(data) {
p <- ggplot(data, aes(x=X1, y=X2)) + 
    stat_bin2d(bins=50) + 
    scale_fill_gradient2(low=palette[4], mid=palette[3], high=palette[2]) +
    xlab("Percentage x") +
    ylab("Percentage y") +
    scale_y_continuous(labels = percent) +
    scale_x_continuous(labels = percent) +
    theme_bw() + theme(text = element_text(size = 15))
print(p)
}

# Example data
# data$X3 <- with(data, 1-X1-X2)
# data <- data[data$X3 >= 0,]

# Auxiliary function for heatmap3d
count_bin <- function(data, minT, maxT, minR, maxR, minL, maxL) {
    ret <- data
    ret <- with(ret, ret[minT <= X1 & X1 < maxT,])
    ret <- with(ret, ret[minL <= X2 & X2 < maxL,])
    ret <- with(ret, ret[minR <= X3 & X3 < maxR,])
    if(is.na(nrow(ret))) {
        ret <- 0
    } else {
        ret <- nrow(ret)
    }
    ret
}

# Plot 3dimensional histogram in a triangle
# See dataframe data for example of the input dataformat
heatmap3d <- function(data, inc, logscale=FALSE, text=FALSE, plot_corner=TRUE) {
#   When plot_corner is FALSE, corner_cutoff determines where to stop plotting
    corner_cutoff = 1
#   When plot_corner is FALSE, corner_number toggles display of obervations in the corners
#   This only has an effect when text==FALSE
    corner_numbers = TRUE

    count <- 1
    points <- data.frame()
    for (z in seq(0,1,inc)) {
        x <- 1- z
        y <- 0
        while (x>0) {
            points <- rbind(points, c(count, x, y, z))
            x <- round(x - inc, digits=2)
            y <- round(y + inc, digits=2)
            count <- count + 1
        }
        points <- rbind(points, c(count, x, y, z))
        count <- count + 1
    }
    colnames(points) = c("IDPoint","T","L","R")

#   base <- ggtern(data=points,aes(L,T,R)) +
#               theme_bw() + theme_hidetitles() + theme_hidearrows() +
#               geom_point(shape=21,size=10,color="blue",fill="white") +
#               geom_text(aes(label=IDPoint),color="blue")
#   print(base)

    polygons <- data.frame()
    c <- 1
#   Normal triangles
    for (p in points$IDPoint) {
        if (is.element(p, points$IDPoint[points$T==0])) {
            next
        } else {
            pL <- points$L[points$IDPoint==p]
            pT <- points$T[points$IDPoint==p]
            pR <- points$R[points$IDPoint==p]
            polygons <- rbind(polygons, 
                        c(c,p),
                        c(c,points$IDPoint[abs(points$L-pL) < inc/2 & abs(points$R-pR-inc) < inc/2]),
                        c(c,points$IDPoint[abs(points$L-pL-inc) < inc/2 & abs(points$R-pR) < inc/2]))    
            c <- c + 1
        }
    }

# Upside down triangles
    for (p in points$IDPoint) {
        if (!is.element(p, points$IDPoint[points$T==0])) {
            if (!is.element(p, points$IDPoint[points$L==0])) {
                pL <- points$L[points$IDPoint==p]
                pT <- points$T[points$IDPoint==p]
                pR <- points$R[points$IDPoint==p]
                polygons <- rbind(polygons, 
                            c(c,p),
                            c(c,points$IDPoint[abs(points$T-pT) < inc/2 & abs(points$R-pR-inc) < inc/2]),
                            c(c,points$IDPoint[abs(points$L-pL) < inc/2 & abs(points$R-pR-inc) < inc/2])) 
                c <- c + 1
            }
        }
    }

#   IMPORTANT FOR CORRECT ORDERING.
    polygons$PointOrder <- 1:nrow(polygons)
    colnames(polygons) = c("IDLabel","IDPoint","PointOrder")

    df.tr <- merge(polygons,points)

    Labs = ddply(df.tr,"IDLabel",function(x){c(c(mean(x$T),mean(x$L),mean(x$R)))})
    colnames(Labs) = c("Label","T","L","R")

#   triangles <- ggtern(data=df.tr,aes(L,T,R)) +
#                   geom_polygon(aes(group=IDLabel),color="black",alpha=0.25) +
#                   geom_text(data=Labs,aes(label=Label),size=4,color="black") +
#                   theme_bw()
#        print(triangles)

    bins <- ddply(df.tr, .(IDLabel), summarize, 
                maxT=max(T),
                maxL=max(L),
                maxR=max(R),
                minT=min(T),
                minL=min(L),
                minR=min(R))

    count <- ddply(bins, .(IDLabel), summarize, N=count_bin(data, minT, maxT, minR, maxR, minL, maxL))
    df <- join(df.tr, count, by="IDLabel")

    Labs = ddply(df,.(IDLabel,N),function(x){c(c(mean(x$T),mean(x$L),mean(x$R)))})
    colnames(Labs) = c("Label","N","T","L","R")

    if (plot_corner==FALSE){
        corner <- ddply(df, .(IDPoint, IDLabel), summarize, maxperc=max(T,L,R))
        corner <- corner$IDLabel[corner$maxperc>=corner_cutoff]

        df$N[is.element(df$IDLabel, corner)] <- 0
        if (text==FALSE & corner_numbers==TRUE) {
            Labs$N[!is.element(Labs$Label, corner)] <- ""
            text=TRUE
        }
    }    

    heat <- ggtern(data=df,aes(L,T,R)) +
        geom_polygon(aes(fill=N,group=IDLabel),color="black",alpha=1)
    if (logscale == TRUE) {
            heat <- heat + scale_fill_gradient(name="Observations", trans = "log",
                            low=palette[2], high=palette[4])
    } else {
            heat <- heat + scale_fill_gradient(name="Observations", 
                            low=palette[2], high=palette[4])
    }
    heat <- heat +
        Tlab("x") +
        Rlab("y") +
        Llab("z") +
        theme_bw() + 
        theme(axis.tern.arrowsep=unit(0.02,"npc"), #0.01npc away from ticks ticklength
                    axis.tern.arrowstart=0.25,axis.tern.arrowfinish=0.75,
                    axis.tern.text=element_text(size=12),
                    axis.tern.arrow.text.T=element_text(vjust=-1),
                    axis.tern.arrow.text.R=element_text(vjust=2),
                    axis.tern.arrow.text.L=element_text(vjust=-1),
                    axis.tern.arrow.text=element_text(size=12),
                    axis.tern.title=element_text(size=15))
    if (text==FALSE) {
        print(heat)
    } else {
        print(heat + geom_text(data=Labs,aes(label=N),size=3,color="white"))
    }
}

# Usage examples
# heatmap3d(data, 0.2, text=TRUE)
# heatmap3d(data, 0.05)
# heatmap3d(data, 0.1, text=FALSE, logscale=TRUE)
# heatmap3d(data, 0.1, text=TRUE, logscale=FALSE, plot_corner=FALSE)
# heatmap3d(data, 0.1, text=FALSE, logscale=FALSE, plot_corner=FALSE)
'''


















------------------------------------------------------------------------------------


```{r}
library(ggplot2)
library(ggridges)

# Create a ridgeline plot directly from wide format
ggplot() +
  geom_density_ridges(
    data = sd, aes(x = `for`, y = "for", fill = source), alpha = 0.8
  ) +
  geom_density_ridges(
    data = sd, aes(x = neutral, y = "neutral", fill = source), alpha = 0.8
  ) +
  geom_density_ridges(
    data = sd, aes(x = against, y = "against", fill = source), alpha = 0.8
  ) +
  labs(title = "Ridgeline Plot of Probabilities by Source and Stance",
       x = "Probability",
       y = "Stance",
       fill = "Source") +
  theme_minimal()

```


```{r}
library(ggplot2)

# Filter the data for CNN
sd_left <- sd[sd$leaning == "Left", ]

# Create a faceted density plot for CNN
ggplot(sd_left) +
  geom_density(aes(x = `for`, fill = "for"), alpha = 0.6) +
  geom_density(aes(x = `neutral.toward`, fill = "neutral"), alpha = 0.6) +
  geom_density(aes(x = against, fill = "against"), alpha = 0.6) +
  scale_fill_manual(values = c("for" = "blue", "neutral" = "green", "against" = "red"),
                    labels = c("For", "Neutral", "Against"),
                    name = "Stance") +
  labs(title = "Probability Distribution of Stances (CNN Only)",
       x = "Probability of being neutral??",
       y = "Density") +
  theme_minimal()

```




```{r}
library(ggplot2)

# Filter the data for CNN
sd_right <- sd[sd$leaning == "Right", ]

# Create a faceted density plot for CNN
ggplot(sd_right) +
  geom_density(aes(x = `for`, fill = "for"), alpha = 0.6) +
  geom_density(aes(x = `neutral.toward`, fill = "neutral"), alpha = 0.6) +
  geom_density(aes(x = against, fill = "against"), alpha = 0.6) +
  scale_fill_manual(values = c("for" = "blue", "neutral" = "green", "against" = "red"),
                    labels = c("For", "Neutral", "Against"),
                    name = "Stance") +
  labs(title = "Probability Distribution of Stances (CNN Only)",
       x = "Probability of being neutral??",
       y = "Density") +
  theme_minimal()

```













```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

# Filter for CNN
sd_cnn <- sd[sd$source == "CNN", ]

# Calculate total expected counts and uncertainty
cnn_summary <- sd_cnn %>%
  summarise(
    total_for = sum(`for`),
    total_neutral = sum(neutral),
    total_against = sum(against),
    sd_for = sd(`for`),
    sd_neutral = sd(neutral),
    sd_against = sd(against)
  ) %>%
  pivot_longer(cols = everything(), 
               names_to = c(".value", "stance"), 
               names_pattern = "(total|sd)_(.*)")

# Bar plot with uncertainty (error bars)
ggplot(cnn_summary, aes(x = stance, y = total, fill = stance)) +
  geom_bar(stat = "identity", width = 0.6, alpha = 0.8) +
  geom_errorbar(aes(ymin = total - sd, ymax = total + sd), width = 0.2, color = "black") +
  scale_fill_manual(values = c("for" = "blue", "neutral" = "green", "against" = "red")) +
  labs(title = "Uncertainty in Stance Classification (CNN Only)",
       x = "Stance",
       y = "Expected Number of Articles",
       fill = "Stance") +
  theme_minimal()

```



```{r}
# Group data by source and stance, and count the number of articles
summary_counts <- sd %>%
  group_by(source, stance) %>%
  summarise(article_count = n(), .groups = "drop")

# Bar plot with side-by-side bars
ggplot(summary_counts, aes(x = stance, y = article_count, fill = source)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.6) +
  scale_fill_manual(values = c("CNN" = "blue", "Fox News" = "red")) +
  labs(title = "Number of Articles by Source and Stance",
       x = "Stance",
       y = "Number of Articles",
       fill = "Source") +
  theme_minimal()

```



```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

# Group data by source and stance, and count the number of articles
summary_counts <- sd %>%
  group_by(source, stance) %>%
  summarise(article_count = n(), .groups = "drop") %>%
  # Ensure all combinations of source and stance are present
  complete(source = c("CNN", "Fox News"), stance = c("for", "neutral", "against"), fill = list(article_count = 0))

# Bar plot with side-by-side bars
ggplot(summary_counts, aes(x = stance, y = article_count, fill = source)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.6) +
  scale_fill_manual(values = c("CNN" = "blue", "Fox News" = "red")) +
  labs(title = "Number of Articles by Source and Stance",
       x = "Stance",
       y = "Number of Articles",
       fill = "Source") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Keep stance names horizontal

```


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

# Reshape data into long format for probabilities
sd_long <- sd %>%
  pivot_longer(cols = c(`for`, neutral, against), 
               names_to = "stance", 
               values_to = "probability")

# Create violin plot
ggplot(sd_long, aes(x = stance, y = probability, fill = source)) +
  geom_violin(trim = FALSE, alpha = 0.6) +
  scale_fill_manual(values = c("CNN" = "blue", "Fox News" = "red")) +
  labs(title = "Uncertainty in Stance Probabilities by Source",
       x = "Stance",
       y = "Probability",
       fill = "Source") +
  theme_minimal()

```


```{r}
colnames(sd)
```



```{r}
# Reshape data into long format
sd_long <- sd %>%
  pivot_longer(
    cols = c(`for`, neutral, against), 
    names_to = "stance_type",  # Avoids conflict with existing "stance" column
    values_to = "probability"
  )

# Create violin plot
ggplot(sd_long, aes(x = stance_type, y = probability, fill = source)) +
  geom_violin(trim = FALSE, alpha = 0.6) +
  scale_fill_manual(values = c("CNN" = "blue", "Fox News" = "red")) +
  labs(title = "Uncertainty in Stance Probabilities by Source",
       x = "Stance",
       y = "Probability",
       fill = "Source") +
  theme_minimal()

```




















